Constructing a universe for the setoid model

### 2020-07-06 paper.tex
small fixes

In Section~\ref{setoid-universe} we discuss the setoid model and various design
choices related to it. We then recall inductive-recursive universes, and the way
they can be equivalently defined as a plain inductive definition, in
Section~\ref{ir-universes}.
%
We then provide, in Section~\ref{ir-setoid-universe}, a first complete
definition of the setoid universe using a form of induction-recursion. This is
followed by an alternative definition of the universe in
Section~\ref{ii-universe}, that does not rely on induction-recursion but instead
on infinitary induction-induction. This inductive-inductive encoding of the
universe is obtained from the inductive-recursive one, following the method of
Section~\ref{ir-universes}.
%
We end the series of universe constructions with
Section~\ref{inductive-universe}, where we outline a purely inductive definition
of the setoid universe, obtained from the inductive-inductive one.

@@

An exceptional aspect of the metatheory used in this paper is the presence of a
proof-irrelevant identity type with a strong transport rule allowing to
eliminate into arbitrary types.
%
In \cite{abel:nbe09}, Abel given a proof of normalization by evaluation for the
Logical Framework extended with a similar proof-irrelevant equality type.
%
Abel and Coquand show in \cite{abel2019failure} that the combination of
impredicativity with a strong transport rule results in terms that fail to
normalize.

>>>>

In Section~\ref{setoid-universe} we discuss the setoid model and various design
choices related to it. We then recall inductive-recursive universes, and the way
they can be equivalently defined as a plain inductive definition, in
Section~\ref{ir-universes}.
%
We then provide, in Section~\ref{ir-setoid-universe}, a first complete
definition of the setoid universe using a special form of induction-recursion.
This form of induction-recursion is not known to be reducible to plain inductive types.
Then we describe an alternative definition of the universe in
Section~\ref{ii-universe}, that does not rely on induction-recursion but instead
on infinitary induction-induction. This inductive-inductive encoding of the
universe is obtained from the inductive-recursive one, following the method of
Section~\ref{ir-universes}.
%
We end the series of universe constructions with
Section~\ref{inductive-universe}, where we outline a purely inductive definition
of the setoid universe, obtained from the inductive-inductive one.

@@

An exceptional aspect of the metatheory used in this paper is the presence of a
proof-irrelevant identity type with a strong transport rule allowing to
eliminate into arbitrary types.
%
In \cite{abel:nbe09}, Abel gives a proof of normalization for the
Logical Framework extended with a similar proof-irrelevant equality type.
%
Abel and Coquand show in \cite{abel2019failure} that the combination of
impredicativity with a strong transport rule results in terms that fail to
normalize.
